Outflows and rotation in Lyman alpha galaxies

### 2017-03-28 paper/paper.tex
new sections

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[An atypical \lya\ dwarf galaxy]{
Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy}
\author[J.E. Forero-Romero et al.]{
  Maria Camila Remolina-Guti\'errez$^1$ \&
  Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co}\\
  %%
  $^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

       %\vspace*{6pt}\\

       %}
       \maketitle

@@

In this paper we present for the first time a study of the joint
effects of galaxy outflows and rotation.
We study a simplified geometrical configuration corresponding to an
spherical gas cloud with symmetrical radial outflows and a rotation
profile corresponding to a solid body.

Our main goal with this work is to measure the effect of the model's
physical parameters on the outgoing \lya line.
In this case, due to
the resonant\footnote{Resonant is a common term used in radiative
  transfer. It means that the photons that create the line are
  absorbed and re-emitted several times before escaping the cloud of
  gas.} nature of the \lya line, analytical solutions can not be
derived. Because of this, it becomes necessary to run simulations that
explore and test the model. In this paper we use the radiative
transfer code \textbf{CLARA} (Code for Lyman Alpha Radiation Analysis)
written by Forero-Romero et al. \cite{CLARA}. CLARA can simulate the
\lya line of a spherical rotating LAE depending on its mass and
velocity, so we modify it to include outflows and then we explore the
resulting consequences on the \lya line. \\

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[Outflows and rotation in LAEs]{
Outflows and rotation in Lyman alpha galaxies}
\author[M.C. Remolina-Gutierrez \& J.E. Forero-Romero]{
  Maria Camila Remolina-Guti\'errez$^1$ \&
  Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co}\\
  %%
  $^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

\maketitle

@@

In this paper we present for the first time a study of the joint
effects of galaxy outflows and rotation.
We study a simplified geometrical configuration corresponding to an
spherical gas cloud with symmetrical radial outflows and a rotation
profile corresponding to a solid body.
We base our modelling on a Monte-Carlo radiative transfer code called
CLARA (Code for Lyman Alpha Radiation Analysis) presented for the
first time in \cite{CLARA}.
Besides modelling the impact of joint rotation and outflows, we also
want to check to what extent the analytical model presented by
\cite{Garavito14} to explain the effects of rotation can also be
applied in our case.

In this paper we introduce first our theoretical tools and assumptions
in Section \ref{sec:theory}, then we present the numerical results and
comparisons against the analytical solution in \ref{sec:results}.
In Section \ref{sec:discussion} we discuss our results and their
possible implications for observational analysis to finally present
our conclusions in Section \ref{sec:conclusions}.

\section{Theoretical Models}
\label{sec:theory}

\subsection{Monte-Carlo Radiative Transfer Model}

\subsection{Analytical Model for Bulk Rotation}

\subsection{Monte-Carlo Radiative Transfer Model}

\subsection{Analytical Model for Bulk Rotation}

\section{Discussion}
\label{sec:discussion}

\subsection{Theoretical Insights}

\subsection{Observational Perspectives}
